---
title: "Airbnb"
author: "chadNoliver"
date: "2019.07.29"
---


This file will be used for exploratory data analysis of New Orleans Airbnb data.
The first analysis will examine the rate at which STR applications have been filed.


```{r, load dependencies, warning=FALSE, comment=FALSE, message=FALSE}
library(RSocrata)
library(knitr)
library(magrittr)
library(dplyr)
```

First we will import the data from the following 3 sources:
  
  1) Open Data STR Licenses - ```open.license```
  2) Inside Airbnb - ```inside.airbnb```
  3) Assessor's Office - ```assessor```

```{r, load data, comment=FALSE, message=FALSE}

#1. Open Data STR Licenses

open.license <- read.socrata(
  "https://data.nola.gov/resource/en36-xvxg.json"
)

kable(open.license %>% 
        group_by(license_type, current_status) %>% 
        filter(current_status=="Issued") %>% 
        summarize(count=n())
)


 
#2. Inside Airbnb

inside.airbnb <- read.csv("data/listings.csv")

kable(head(inside.airbnb %>% 
             select(-c(summary, space, description, notes, host_about, neighborhood_overview, transit:house_rules))
           )
      ) 
```


Next we will join the ```open.license``` table with the ```inside.airbnb``` table to identify which ```inside.airbnb$id``` have ```inside.airbnb$license``` that match with ```open.license$license_number```

Steps will include:
  1) Clean ```inside.airbnb``` data to only inlude appropriate license #'s
   - matches should be ```\\d{2}STR-\\d{5}```

```{r, comment=FALSE, message=FALSE}

#1. Find only the actual license numbers

#pattern <- "\\d{2}STR\\d{5}|\\d{2}-STR\\d{5}|\\d{2}STR-\\d{5}|\\d{2}-STR-\\d{5}"
pattern <- "\\d{2}STR-\\d{5}"
library(stringr)
inside.airbnb <- inside.airbnb %>%
  mutate(license.alt = str_to_upper(str_remove_all(license,"[[:space:]]"))) %>%
  mutate(license.match = str_match(license.alt, pattern))
           
kable(head(inside.airbnb %>% 
       select(license, license.alt, license.match)
)) 

```

 2) Clean ```open.license```

```{r, comment=FALSE, message=FALSE}

open.inside <- inside.airbnb %>% 
  filter (license.match!="NA") %>% 
  left_join(filter(open.license, license_number!="NA"), by=c("license.match" = "license_number"))

kable(head(open.inside %>% 
             select(-c(space, description, notes, host_about, amenities, summary, neighborhood_overview, transit:house_rules)
                    )
           )
      )

kable(head(open.inside %>% 
  group_by(host_id) %>% 
  summarize(count=n()) %>% 
  arrange(desc(count))
  )
)
kable(head(open.inside %>% 
  group_by(host_name) %>% 
  summarize(count=n()) %>% 
  arrange(desc(count))
  )
)



kable(head(open.license %>% 
        group_by(license_number) %>%  
        summarize(count = n()) %>% 
        arrange(desc(count)))
)
```
 

Next we will hardcode the str ```zoning.key``` from  https://www.nola.gov/short-term-rentals/str-zoning-restrictions/where-are-strs-allowed/ (as represented 2019.08.01)


```{r, comment=FALSE, message=FALSE}

zoning.key <- rbind(
c("BIP", 	"P", NA , NA), 	  	  
c("C-1", 	"P", 	"P", 	"P"),
c("C-2", 	"P", 	"P", 	"P"),
c("C-3", 	"P", 	"P", 	"P"),
c("CBD-1", 	"P", 	"*", 	"P*"),
c("CBD-2", 	"P", 	"*", 	"P*"),
c("CBD-3", 	"P", 	"*", 	"P*"),
c("CBD-4", 	"P", 	"*", 	"P*"),
c("CBD-5", 	"P", 	"*", 	"P*"),
c("CBD-6", 	"P", 	"*", 	"P*"),
c("CBD-7", 	"P", 	"*", 	"P*"),
c("EC", 	"P", 	"P", 	"P"),
c("HI", 	"P", NA, NA),
c("HMC-1", 	"P", 	"*", 	"P*"),
c("HMC-2", 	"P", 	"*", 	"P*"),
c("HM-MU", 	"P", 	"*", 	"P*"),
c("HMR-1", 	"P", 	"*", NA), 	 
c("HMR-2", 	"P", 	"*", NA), 	 
c("HMR-3", 	"P", 	"*", NA), 	 
c("HU-B1", 	"P", 	"*", 	"P*"),
c("HU-B1A", 	"P", 	"*", 	"C*"),
c("HU-MU", 	"P", 	"*", 	"P*"),
c("HU-RD1", 	"P", 	"*", NA), 	 
c("HU-RD2", 	"P", 	"*", NA), 	 
c("HU-RM1", 	"P", 	"*", NA), 	 
c("HU-RM2", 	"P", 	"*", NA), 	 
c("HU-RS", 	"P", 	"*", NA), 	 
c("LI", 	"P", 	"P", NA), 	 
c("LS", 	"P", 	"P", 	"P"),
c("MC", 	"P", 	"P", 	"P"),
c("MI", 	"P", NA, NA), 	  	 
c("M-MU", 	"P", 	 NA, 	"P"),
c("MS", 	"P", NA, NA), 	  	 
c("MU-1", 	"P", 	"*", 	"P*"),
c("MU-2", 	"P", 	"*", 	"P*"),
c("R-RE", 	"P", NA, NA), 	  	 
c("S-B1", 	"P", NA, "P"),
c("S-B2", 	"P", NA,	"P"),
c("S-LB1", 	"P", 	"P", 	"P"),
c("S-LB2", 	"P", 	"P", 	"P"),
c("S-LC", 	"P", 	"P", 	"P"),
c("S-LM", 	"P", 	"P", 	"P"),
c("S-LP", 	"P", NA, NA), 	  	 
c("S-LRD1", 	"P", 	"P", NA), 	 
c("S-LRD2", 	"P", 	"P", NA), 	 
c("S-LRM1", 	"P", 	"P", NA), 	 
c("S-LRM2", 	"P", 	"P", NA), 	 
c("S-LRS1", 	"P", 	"P", NA), 	 
c("S-LRS2", 	"P", 	"P", NA), 	 
c("S-LRS3", 	"P", 	"P", NA), 	 
c("S-RD", 	"P", 	"P", NA), 	 
c("S-RM1", 	"P", 	"P", NA), 	 
c("S-RM2", 	"P", 	"P", NA), 	 
c("S-RS", 	"P", 	"P", NA), 	 
c("VCC-1", NA, NA, NA), 	  	  	 
c("VCC-2", NA, NA, NA), 	  	  	 
c("VCE", NA, NA, "P*"),
c("VCE-1", NA, NA, NA), 	  	  	 
c("VCP", NA, NA, NA), 	  	  	 
c("VCR-1", NA, NA, NA), 	  	  	 
c("VCR-2", NA, NA, NA), 	  	  	 
c("VCS", NA, NA, NA), 	  	  	 
c("VCS-1", NA, NA, NA)
)

colnames(zoning.key) <- c("Zoning District", "Accessory STR","Temporary STR", "Commercial STR")

kable(head(zoning.key))


zoning.key.kgp <- rbind(
  #Zoning Type | Zoning Code | Zoning Code Description | Bed and Breakfast - Accessory | Bed and Breakfast - Primary | Large | Small | Hostel | Hotel/Motel | Commercial
#Open Space Districts
                        c("Open Space Districts", "OS-N",  "Neighborhood Open Space District","N","N","N","N","N","N","N"),
                        c("Open Space Districts", "OS-G", "Greenway Open Space District", "N", "N", "N", "N","N","N","N"),
                        c("Open Space Districts", "OS-R", "Regional Open Space District", "N", "N", "N", "N","N","N","N"),
                        c("Open Space Districts", "NA", "Natural Areas District", "N", "N", "N", "N","N","N","N"),
                        c("Open Space Districts", "GPD", "General Planned Development District", "N", "N", "N", "N","N","C","C"),
#Rural Development Districts
                        c("Rural Development Districts", "R-RE", "Rural Residental Estate District", "P", "N", "N", "P","N","N","N"),
                        c("Rural Development Districts", "M-MU", "Maritime Mixed-Use District", "P", "P", "P", "P","N","N","P"),
#Historic Core Neighborhoods Districts
                        c("Historic Core Neighborhoods Districts", "VCR-1", "Vieux Carré Residential District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "VCR-2", "Vieux Carré Residential District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "HMR-1", "Historic Marigny/Tremé/Bywater Residential District", "P", "C", "C", "P","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "HMR-2", "Historic Marigny/Tremé/Bywater Residential District", "P", "C", "C", "P","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "HMR-3", "Historic Marigny/Tremé/Bywater Residential District", "P", "C", "C", "P","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "VCC-1", "Vieux Carré Commercial District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "VCC-2", "Vieux Carré Commercial District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "VCE", "Vieux Carré Entertainment District", "P", "P", "P", "P","N","N","P"),
                        c("Historic Core Neighborhoods Districts", "VCE-1", "Vieux Carré Entertainment District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "VCS", "Vieux Carré Service District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "VCS-1", "Vieux Carré Service District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "VCP", "Vieux Carré Park District", "N", "N", "N", "N","N","N","N"),
                        c("Historic Core Neighborhoods Districts", "HMC-1", "Historic Marigny/Tremé/Bywater Commercial District", "P", "P", "P", "P","","","C"),
                        c("Historic Core Neighborhoods Districts", "HMC-2", "Historic Marigny/Tremé/Bywater Commercial District", "P", "P", "P", "P","P","P","P"),
                        c("Historic Core Neighborhoods Districts", "HM-MU", "Historic Marigny/Tremé/Bywater Mixed-Use District", "P", "P", "P", "P","N","C","P"),

#Historic Urban Neighborhoods Districts

                        c("Historic Urban Neighborhoods Districts","HU-RS", "Single-Family Residential District", "P", "N", "N", "P", "N","N","N"),
                        c("Historic Urban Neighborhoods Districts","HU-RD1", "Two-Family Residential District", "P", "N", "N", "P", "N","N","N"),
                        c("Historic Urban Neighborhoods Districts","HU-RD2", "Two-Family Residential District", "P", "N", "N", "P", "N","N","N"),
                        c("Historic Urban Neighborhoods Districts","HU-RM1", "Multi-Family Residential District", "P", "C", "P", "P", "N","N","N"),
                        c("Historic Urban Neighborhoods Districts","HU-RM2", "Multi-Family Residential District", "P", "C", "P", "P", "N","N","N"),
                        c("Historic Urban Neighborhoods Districts","HU-B1A", "Neighborhood Business District", "P", "P", "P", "P", "N","N","N"),
                        c("Historic Urban Neighborhoods Districts","HU-B1", "Neighborhood Business District", "P", "P", "P", "P", "N","N","N"),
                        c("Historic Urban Neighborhoods Districts","HU-MU", "Neighborhood Mixed-Use District", "P", "P", "P", "P", "N","N","P"),
# Suburban Neighborhoods
                        c("Suburban Neighborhoods", "S-RS", "Single-Family Residential District", "P", "N", "N", "P","N","N","N"),
                        c("Suburban Neighborhoods", "S-RD", "Two-Family Residential District", "P", "N", "N", "P","N","N","N"),
                        c("Suburban Neighborhoods", "S-RM1", "Multi-Family Residential District", "P", "N", "N", "P","N","N","N"),
                        c("Suburban Neighborhoods", "S-RM2", "Multi-Family Residential District", "P", "N", "N", "P","N","N","N"),
                        c("Suburban Neighborhoods", "S-LRS1", "Lakeview Single-Family Residential District", "P", "N", "N", "P","N","N","N"),
                        c("Suburban Neighborhoods", "S-LRS2", "Lake Vista and Lake Shore Single-Family Residential District", "N", "N", "N", "N","N","N","N"),
                        c("Suburban Neighborhoods", "S-LRS3", "Lakewood and Country Club Gardens Single-Family Residential District", "N", "N", "N", "N","N","N","N"),
                        c("Suburban Neighborhoods", "S-LRD1", "Lake Vista Two-Family Residential District", "N", "N", "N", "N","N","N","N"),
                        c("Suburban Neighborhoods", "S-LRD2", "Lakewood/Parkview Two-Family Residential District", "C", "N", "N", "C","N","N","N"),
                        c("Suburban Neighborhoods", "S-LRM1", "Lake Area Low-Rise Multi-Family Residential District", "C", "N", "N", "C","N","N","N"),
                        c("Suburban Neighborhoods", "S-LRM2", "Lake Area High-Rise Multi-Family Residential District", "C", "N", "N", "C","N","N","N"),
                        c("Suburban Neighborhoods", "S-B1", "Suburban Business District", "N", "N", "N", "N","N","N","N"),
                        c("Suburban Neighborhoods", "S-B2", "Pedestrian-Oriented Corridor Business District", "N", "N", "N", "N","N","N","P"),
                        c("Suburban Neighborhoods", "S-LB1", "Lake Area Neighborhood Business District", "P", "P", "P", "P","N","N","N"),
                        c("Suburban Neighborhoods", "S-LB2", "Lake Area Neighborhood Business District", "P", "P", "P", "P","N","N","P"),
                        c("Suburban Neighborhoods", "S-LC", "Lake Area General Commercial District", "P", "P", "P", "P","N","C","P"),
                        c("Suburban Neighborhoods", "S-LP", "Lake Area Neighborhood Park District", "N", "N", "N", "N","N","N","N"),
                        c("Suburban Neighborhoods", "S-LM", "Lake Area Marina District", "N", "N", "N", "N","N","C","P"),
                        c("Suburban Neighborhoods", "S-MU", "Suburban Neighborhood Mixed-Use District", "C", "N", "N", "P","N","N","N"),
 #Commercial Center and Institutional Campus Districts

                        c("Commercial Center and Institutional Campus Districts", "C-1", "General Commercial District", "N", "N", "N", "N","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "C-2", "Auto-Oriented Commercial District", "N", "N", "N", "N","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "C-3", "Heavy Commercial District", "N", "N", "N", "N","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "MU-1", "Medium Intensity Mixed-Use District", "P", "P", "P", "P","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "MU-2", "High Intensity Mixed-Use District", "P", "P", "P", "P","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "EC", "Educational Campus District", "P", "N", "N", "N","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "MC", "Medical Campus District", "N", "N", "N", "N","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "MS", "Medical Service District", "N", "N", "N", "N","N","P","P"),
                        c("Commercial Center and Institutional Campus Districts", "LS", "Life Science Mixed-Use District", "N", "N", "N", "N","N","P","P"),
#Centers for Industry
                        c("Centers for Industry", "LI", "Light Industrial District", "N", "N", "N", "N","N","P","P"),
                        c("Centers for Industry", "HI", "Heavy Industrial District", "N", "N", "N", "N","N","C","C"),
                        c("Centers for Industry", "MI", "Maritime Industrial District", "N", "N", "N", "N","N","P","C"),
                        c("Centers for Industry", "BIP", "Business-Industrial Park District", "N", "N", "N", "N","N","P","P"),

#Central Business District

                        c("Central Business District", "CBD-1", "Core Central Business District", "P", "P", "P", "P","N","P","P"),
                        c("Central Business District", "CBD-2", "Historic Commercial and Mixed-Use District", "P", "P", "P", "P","N","P","P"),
                        c("Central Business District", "CBD-3", "Cultural Arts District", "P", "P", "P", "P","N","P","P"),
                        c("Central Business District", "CBD-4", "Exposition District", "N", "N", "N", "N","N","P","P"),
                        c("Central Business District", "CBD-5", "Urban Core Neighborhood Lower Intensity Mixed-Use District", "P", "P", "P", "P","N","C","C"),
                        c("Central Business District", "CBD-6", "Urban Core Neighborhood Mixed-Use District", "P", "P", "P", "P","N","P","P"),
                        c("Central Business District", "CBD-7", "Bio-Science District", "P", "P", "P", "P","N","P","P")
 
 #Overlay Zoning Districts
                        #c("Overlay Zoning Districts", "SC", "Suburban Corridor Use Restriction Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "ENORC", "Eastern New Orleans Renaissance Corridor Use Restriction Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "HUC", "Historic Urban Corridor Use Restriction Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "???", "Lower St. Charles Avenue Use Restriction Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "RDO-1", "Residential Diversity Overlay District (Marigny/Bywater)", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "RDO-2", "Residential Diversity Overlay District (Tremé/Seventh Ward)", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "AC-1", "Arts and Culture Diversity Overlay District (Frenchmen, St. Bernard, Broad)", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "AC-2", "Arts and Culture Diversity Overlay District (Freret, Newton, Teche)", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "AC-3", "Arts and Culture Diversity Overlay District (St. Claude)", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "AC-4", "Arts and Culture Diversity Overlay District (Tremé)", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "RIV", "Riverfront Design Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "CPC", "Character Preservation Corridor Design Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "EC", "Enhancement Corridor Design Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "CT", "Corridor Transformation Design Overlay District", "", "", "", "","","",""),
                        #c("Overlay Zoning Districts", "GC", "Greenway Corridor Design Overlay District", "", "", "", "","","","")
)

 
 
colnames(zoning.key.kgp) <- c("Zoning Group", "Zoning Code", "Zoning Code Description","Bed and Breakfast - Accessory","Bed and Breakfast - Primary", "Large", "Small", "Hostel", "Hotel/Motel","Commercial")
         
kable(zoning.key.kgp)

```
 

Code below used for importing CZO effective until 2019.12.01
```{r comment=FALSE, message=FALSE}

library(readxl)

import.czo <- function(c){
  c <- read_excel(path="data/CZO Key.xlsx",sheet=shQuote(c))
  stack.c <- c %>%
    select(-`USE STANDARDS`) %>% 
    t()
kable(head(stack.c))
}


import.czo(table07.1)
print(stack.table07.1)
```

Council meeting notes:
 - Licenses are only valid for 1 yr - not transferrable
 - Three types:
 -- Small
 -- Large has up to 3 entire dwelling unnits
 -- Commercial - up to 5 bedrooms, not 10 occupants
 - 10A Amendmnet
 - 10B Amendment
 - Operator permits
 - Look into VC-1 Ban (likely VCR-1)
 - Look into HUB-1 Zoning
- CBD-5
 
